Reading information from the American Community Survey into R

### 2024-07-06 text/20/non-breaking-spaces.Rmd
Updated rmd files

---
title: "Identifying and manipulating non-breaking spaces"
author: "Steve Simon"
source: new
date: "2020-01-07"
categories:
- Blog post
tags:
- Data management
output: html_document
---

@@

```{r insert}
tst1 <- "?"
tst1
```

@@

```{r chartoraw}
charToRaw(tst1)
```

@@

```{r search}
tst1=="\xa0"
```

>>>>

---
title: "Identifying and manipulating non-breaking spaces"
author: "Steve Simon"
source: new
date: "2020-01-07"
categories:
- Blog post
tags:
- Data management
- Rmarkdown code
output: html_document
page_update: partial
---

@@

```{r  non-breaking-spaces-01}
tst1 <- "?"
tst1
```

@@

```{r  non-breaking-spaces-02}
charToRaw(tst1)
```

@@

```{r  non-breaking-spaces-03}
tst1=="\xa0"
```

### 2024-07-06 text/20/poor-color-choice.Rmd
Updated rmd files

---
title: "An example of a poor color choice"
author: "Steve Simon"
source: new
date: "2020-03-11"
categories:
- Blog post
tags:
- Graphical display
output: html_document
---

@@

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo=FALSE, fig.width=5, fig.height=5)
```

```{r color-circle1, echo=FALSE, fig.width=5, fig.height=5}
suppressMessages(suppressWarnings(library(ggplot2)))
suppressMessages(suppressWarnings(library(RColorBrewer)))
n <- 500
k <- 5
delta <- 0.9
angle_seq <- (1:n)/n
df0<- data.frame(
    x=delta*sin(2*pi*angle_seq),
    y=delta*cos(2*pi*angle_seq))
sb <- (n/k)*(1:k)
df1 <- df0[sb, ]

@@

```{r color-circle2, echo=FALSE, fig.width=5, fig.height=5}
ggplot(df0, aes(x, y)) +
  geom_point(
      color=hsv(angle_seq, 1, 0.5), 
      size=2, 
      shape=16) +
  geom_point(
      data=df1, 
      aes(x, y), 
      color=hsv(sb/n, 1, 0.5), 
      size=24, 
      shape=16) +
  expand_limits(
      x=c(-1, 1), 
      y=c(-1, 1)) +
  theme_void() +
  theme(
      panel.background = 
          element_rect(fill="#808080"))
```

@@

```{r color-circle3, echo=FALSE, fig.width=5, fig.height=5}
ggplot(df0, aes(x, y)) +
  geom_point(
      color=hsv(angle_seq, 0.5, 1), 
      size=2, 
      shape=16) +
  geom_point(
      data=df1, 
      aes(x, y), 
      color=hsv(sb/n, 0.5, 1), 
      size=24, 
      shape=16) +
  expand_limits(
      x=c(-1, 1), 
      y=c(-1, 1)) +
  theme_void() +
  theme(
      panel.background =
          element_rect(fill="#808080"))
```

@@

```{r brew1, fig.height=1}
par(mar=rep(0, 4))
display.brewer.pal(5, "Set1")
pal5 <- brewer.pal(5, "Set1")
```

>>>>

---
title: "An example of a poor color choice"
author: "Steve Simon"
source: new
date: "2020-03-11"
categories:
- Blog post
tags:
- Graphical display
- Rmarkdown graphs
output: html_document
page_update: complete
---

@@

```{r poor-color-choice-01, echo=FALSE}
knitr::opts_chunk$set(echo=FALSE, fig.width=5, fig.height=5)
```

```{r poor-color-choice-02, echo=FALSE, fig.width=5, fig.height=5}
suppressMessages(suppressWarnings(library(ggplot2)))
suppressMessages(suppressWarnings(library(RColorBrewer)))
n <- 500
k <- 5
delta <- 0.9
angle_seq <- (1:n)/n
df0<- data.frame(
    x=delta*sin(2*pi*angle_seq),
    y=delta*cos(2*pi*angle_seq))
sb <- (n/k)*(1:k)
df1 <- df0[sb, ]

@@

```{r poor-color-choice-03, echo=FALSE, fig.width=5, fig.height=5}
ggplot(df0, aes(x, y)) +
  geom_point(
      color=hsv(angle_seq, 1, 0.5), 
      size=2, 
      shape=16) +
  geom_point(
      data=df1, 
      aes(x, y), 
      color=hsv(sb/n, 1, 0.5), 
      size=24, 
      shape=16) +
  expand_limits(
      x=c(-1, 1), 
      y=c(-1, 1)) +
  theme_void() +
  theme(
      panel.background = 
          element_rect(fill="#808080"))
```

@@

```{r poor-color-choice-04, echo=FALSE, fig.width=5, fig.height=5}
ggplot(df0, aes(x, y)) +
  geom_point(
      color=hsv(angle_seq, 0.5, 1), 
      size=2, 
      shape=16) +
  geom_point(
      data=df1, 
      aes(x, y), 
      color=hsv(sb/n, 0.5, 1), 
      size=24, 
      shape=16) +
  expand_limits(
      x=c(-1, 1), 
      y=c(-1, 1)) +
  theme_void() +
  theme(
      panel.background =
          element_rect(fill="#808080"))
```

@@

```{r poor-color-choice-05, fig.height=1}
par(mar=rep(0, 4))
display.brewer.pal(5, "Set1")
pal5 <- brewer.pal(5, "Set1")
```

### 2024-07-06 text/20/reading-text-files.Rmd
Updated rmd files

---
title: "Reading text files"
author: "Steve Simon"
source: new
date: "2020-04-30"
categories:
- Blog post
tags:
- Data management
output: html_document
---

@@

```{r ascii, echo=FALSE}
symbol_codes <- c(33:126)
symbols <- NULL
for (i in symbol_codes) {symbols <- c(symbols, rawToChar(as.raw(i)))} 
symbols <- setdiff(symbols, LETTERS)
symbols <- setdiff(symbols, letters)
symbols <- setdiff(symbols, as.character(0:9))
```

>>>>

---
title: "Reading text files"
author: "Steve Simon"
source: new
date: "2020-04-30"
categories:
- Blog post
tags:
- Data management
- Rmarkdown code
output: html_document
page_update: partial
---

@@

```{r reading-text-files-01, echo=FALSE}
symbol_codes <- c(33:126)
symbols <- NULL
for (i in symbol_codes) {symbols <- c(symbols, rawToChar(as.raw(i)))} 
symbols <- setdiff(symbols, LETTERS)
symbols <- setdiff(symbols, letters)
symbols <- setdiff(symbols, as.character(0:9))
```

### 2024-07-06 text/20/rmarkdown-papers.Rmd
Updated rmd files

---
title: "How I use R Markdown to write research papers"
source: new
date: "2020-11-21"
categories:
- Blog post
tags:
- Writing research papers
output: html_document
---

@@

```{r, echo=FALSE, fig.width=6, fig.height=3}
suppressMessages(suppressWarnings(library(broom)))
suppressMessages(suppressWarnings(library(knitr)))
suppressMessages(suppressWarnings(library(tidyverse)))
x=seq(-1, 1, length=10000)
y <- x*sin(1/x)
data.frame(x, y) %>%
  ggplot(aes(x, y)) + geom_line()
```

@@

```{r, echo=FALSE}
sz <- 1.2
xc <- 20
yc <- 80
xbox <- 10*c(-1, -1,  1,  1, -1) + xc
ybox <- 10*c(-1,  1,  1, -1, -1) + yc
data.frame(x=xbox, y=ybox) %>%
  ggplot(aes(x, y)) +
  expand_limits(x=c(0, 100), y=c(0, 100)) +
  theme_void() +
  geom_path(size=sz) + 
  geom_text(x=xc, y=yc, label="S") +
  geom_path(x=xbox+30, y=ybox-30, size=sz) +
  geom_text(x=xc+30, y=yc-30, label="I") +
  geom_path(x=xbox+60, y=ybox-60, size=sz) +
  geom_text(x=xc+60, y=yc-60, label="R") +
  geom_curve(
    x=xc+40, y=yc-35, xend=xc+55, yend=30, curvature=-0.3, size=sz, 
    arrow = arrow(type = "closed", length=unit(0.15, "inches"))) -> sir_plot
sir_plot +
  geom_curve(
    x=xc+10, y=yc- 5, xend=xc+25, yend=yc-20, curvature=-0.3, size=sz, 
    arrow = arrow(type = "closed", length=unit(0.15, "inches")))
```

@@

```{r}
lm(breaks ~ wool*tension, data = warpbreaks) %>%
  tidy %>%
  rename(t.test=statistic) %>% 
  kable(
    digits=c(1, 1, 1, 2, 4),
    caption="Analysis of variance table")
```

>>>>

---
title: "How I use R Markdown to write research papers"
source: new
date: "2020-11-21"
categories:
- Blog post
tags:
- R programming
- Rmarkdown graphics
- Writing research papers
output: html_document
page_update: complete
---

@@

```{r rmarkdown-papers-01, echo=FALSE, fig.width=6, fig.height=3}
suppressMessages(suppressWarnings(library(broom)))
suppressMessages(suppressWarnings(library(knitr)))
suppressMessages(suppressWarnings(library(tidyverse)))
x=seq(-1, 1, length=10000)
y <- x*sin(1/x)
data.frame(x, y) %>%
  ggplot(aes(x, y)) + geom_line()
```

@@

```{r rmarkdown-papers-02, echo=FALSE}
sz <- 1.2
xc <- 20
yc <- 80
xbox <- 10*c(-1, -1,  1,  1, -1) + xc
ybox <- 10*c(-1,  1,  1, -1, -1) + yc
data.frame(x=xbox, y=ybox) %>%
  ggplot(aes(x, y)) +
  expand_limits(x=c(0, 100), y=c(0, 100)) +
  theme_void() +
  geom_path(size=sz) + 
  geom_text(x=xc, y=yc, label="S") +
  geom_path(x=xbox+30, y=ybox-30, size=sz) +
  geom_text(x=xc+30, y=yc-30, label="I") +
  geom_path(x=xbox+60, y=ybox-60, size=sz) +
  geom_text(x=xc+60, y=yc-60, label="R") +
  geom_curve(
    x=xc+40, y=yc-35, xend=xc+55, yend=30, curvature=-0.3, size=sz, 
    arrow = arrow(type = "closed", length=unit(0.15, "inches"))) -> sir_plot
sir_plot +
  geom_curve(
    x=xc+10, y=yc- 5, xend=xc+25, yend=yc-20, curvature=-0.3, size=sz, 
    arrow = arrow(type = "closed", length=unit(0.15, "inches")))
```

@@

```{r rmarkdown-papers-03}
lm(breaks ~ wool*tension, data = warpbreaks) %>%
  tidy %>%
  rename(t.test=statistic) %>% 
  kable(
    digits=c(1, 1, 1, 2, 4),
    caption="Analysis of variance table")
```

### 2024-07-06 text/20/smart-quotes.Rmd
Updated rmd files

---
title: "Smart quotes, em dashes, and en dashes"
author: "Steve Simon"
source: new
date: "2020-03-02"
categories:
- Blog post
tags:
- Data management
output: html_document
---

@@

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width=4.5, fig.height=0.5)
suppressMessages(suppressWarnings(library(stringr)))
cplot <- function(x) {
  par(mar=rep(0,4))
  plot(-1:1, -1:1, type="n", axes=FALSE)
  text(-1, 0, x, cex=2, adj=0)
}
```

```{r straight-double-quotes}
cplot('"')
```

@@

```{r straight-single-quotes}
cplot("'")
```

@@

```{r backtick}
cplot("`")
```

@@

```{r assign-double-quotes-1}
cplot("x  < -  ' \" '")
```

@@

```{r assign-double-quotes-2}
cplot('x  < -  \" \\ "\ "')
```

@@

```{r charToRaw-1}
cplot("charToRaw(' \" ')")
```

```{r charToRaw-2}
cplot(charToRaw('"'))
```

@@

```{r charToRaw-3}
cplot("charToRaw(\" ' \")")
```

```{r charToRaw-4}
cplot(charToRaw("'"))
```

@@

```{r charToRaw-5}
cplot("charToRaw(\" ` \")")
```

```{r charToRaw-6}
cplot(charToRaw("`"))
```

@@

```{r convert-hex-1}
cplot('"\\x22"')
```

```{r convert-hex-2}
cplot("\x22")
```

@@

```{r left-double-quote}
cplot("\U201C")
```

@@

```{r right-double-quote}
cplot("\U201D")
```

@@

```{r left-single-quote}
cplot("\U2018")
```

@@

```{r right-single-quote}
cplot("\U2019")
```

@@

```{r rawToChar-8}
cplot('charToRaw( \" \U201C \" )')
```

```{r rawToChar-9}
x <- str_c(as.character(charToRaw("\U201C")), collapse=" ")
cplot(x)
```

@@

```{r accented}
cplot("\U00E9")
```

@@

```{r cedilla}
cplot("\U00C7")
```

@@

```{r tilde}
cplot("\U00F1")
```

@@

```{r sharp-S}
cplot("\U00DF")
```

@@

```{r thorn}
cplot("\U00FE")
```

@@

```{r greek}
cplot("\U03B1 \U03B2 \U03B3")
```

@@

```{r arabic}
cplot("\U062A\U0633\U062C\U0651\U0644")
```

@@

```{r chinese}
cplot("\U4E2D\U6587")
```

@@

```{r emojis}
cplot("\U1F642\U1F622")
```

@@

```{r unicode-1}
cplot("\"\\U201C\"")
```

```{r unicode-2}
cplot("\U201C")
```

@@

```{r unicode-3}
cplot("\"\\U201D\"")
```

```{r unicode-4}
cplot("\U201D")
```

@@

```{r unicode-5}
cplot("\"\\U2018\"")
```

```{r unicode-6}
cplot("\U2018")
```

@@

```{r unicode-7}
cplot("\"\\U2019\"")
```

```{r unicode-8}
cplot("\U2019")
```

@@

```{r minus-1}
cplot("-")
```

@@

```{r em-dash-1}
cplot("\"\\U2014\"")
```

```{r em-dash-2}
cplot("\U2014")
```

@@

```{r en-dash-1}
cplot("\"\\U2013\"")
```

```{r en-dash-2}
cplot("\U2013")
```

@@

There's a [nice web page](https://www.cl.cam.ac.uk/~mgk25/ucs/quotes.html) about the historical developments of computer codes for quote marks and dashes and [another page](https://cran.r-project.org/web/packages/utf8/vignettes/utf8.html) that talks about computer codes in general from the perspective of an R programmer.

There are some other variants, such as the prime symbols, described in [this Wikipedia page](https://en.wikipedia.org/wiki/Prime_(symbol)).

>>>>

---
title: "Smart quotes, em dashes, and en dashes"
author: "Steve Simon"
source: new
date: "2020-03-02"
categories:
- Blog post
tags:
- Data management
- Rmarkdown code
output: html_document
page_update: complete
---

@@

```{r smart-quotes-01, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width=4.5, fig.height=0.5)
suppressMessages(suppressWarnings(library(stringr)))
cplot <- function(x) {
  par(mar=rep(0,4))
  plot(-1:1, -1:1, type="n", axes=FALSE)
  text(-1, 0, x, cex=2, adj=0)
}
```

```{r smart-quotes-02}
cplot('"')
```

@@

```{r smart-quotes-03}
cplot("'")
```

@@

```{r smart-quotes-04}
cplot("`")
```

@@

```{r smart-quotes-05}
cplot("x  < -  ' \" '")
```

@@

```{r smart-quotes-06}
cplot('x  < -  \" \\ "\ "')
```

@@

```{r smart-quotes-07}
cplot("charToRaw(' \" ')")
```

```{r smart-quotes-08}
cplot(charToRaw('"'))
```

@@

```{r smart-quotes-09}
cplot("charToRaw(\" ' \")")
```

```{r smart-quotes-10}
cplot(charToRaw("'"))
```

@@

```{r smart-quotes-11}
cplot("charToRaw(\" ` \")")
```

```{r smart-quotes-12}
cplot(charToRaw("`"))
```

@@

```{r smart-quotes-13}
cplot('"\\x22"')
```

```{r smart-quotes-14}
cplot("\x22")
```

@@

```{r smart-quotes-15}
cplot("\U201C")
```

@@

```{r smart-quotes-16}
cplot("\U201D")
```

@@

```{r smart-quotes-17}
cplot("\U2018")
```

@@

```{r smart-quotes-18}
cplot("\U2019")
```

@@

```{r smart-quotes-19}
cplot('charToRaw( \" \U201C \" )')
```

```{r smart-quotes-20}
x <- str_c(as.character(charToRaw("\U201C")), collapse=" ")
cplot(x)
```

@@

```{r smart-quotes-21}
cplot("\U00E9")
```

@@

```{r smart-quotes-22}
cplot("\U00C7")
```

@@

```{r smart-quotes-23}
cplot("\U00F1")
```

@@

```{r smart-quotes-24}
cplot("\U00DF")
```

@@

```{r smart-quotes-25}
cplot("\U00FE")
```

@@

```{r smart-quotes-26}
cplot("\U03B1 \U03B2 \U03B3")
```

@@

```{r smart-quotes-27}
cplot("\U062A\U0633\U062C\U0651\U0644")
```

@@

```{r smart-quotes-28}
cplot("\U4E2D\U6587")
```

@@

```{r smart-quotes-29}
cplot("\U1F642\U1F622")
```

@@

```{r smart-quotes-30}
cplot("\"\\U201C\"")
```

```{r smart-quotes-31}
cplot("\U201C")
```

@@

```{r smart-quotes-32}
cplot("\"\\U201D\"")
```

```{r smart-quotes-33}
cplot("\U201D")
```

@@

```{r smart-quotes-34}
cplot("\"\\U2018\"")
```

```{r smart-quotes-35}
cplot("\U2018")
```

@@

```{r smart-quotes-36}
cplot("\"\\U2019\"")
```

```{r smart-quotes-37}
cplot("\U2019")
```

@@

```{r smart-quotes-38}
cplot("-")
```

@@

```{r smart-quotes-39}
cplot("\"\\U2014\"")
```

```{r smart-quotes-40}
cplot("\U2014")
```

@@

```{r smart-quotes-41}
cplot("\"\\U2013\"")
```

```{r smart-quotes-42}
cplot("\U2013")
```

@@

There's a [nice web page][kuh1] about the historical developments of computer codes for quote marks and dashes and [another page][utf8] that talks about computer codes in general from the perspective of an R programmer.

There are some other variants, such as the prime symbols, described in [this Wikipedia page][wik1].

[kuh1]: https://www.cl.cam.ac.uk/~mgk25/ucs/quotes.html
[utf8]: https://cran.r-project.org/web/packages/utf8/vignettes/utf8.html
[wik1]: https://en.wikipedia.org/wiki/Prime_(symbol)

### 2024-07-06 text/21/anonymizing-ids.Rmd
Updated rmd files

---
title: "Anonymizing ids"
author: "Steve Simon"
source: new
date: "2021-06-10"
categories:
- Blog post
tags:
- Privacy in research
output: html_document
---

>>>>

---
title: "Anonymizing ids"
author: "Steve Simon"
source: new
date: "2021-06-10"
categories:
- Blog post
tags:
- Privacy in research
- Rmarkdown code
output: html_document
page_update: complete
---

### 2024-07-06 text/21/blogdown-first-steps.Rmd
Updated rmd files

---
title: "First steps with blogdown"
author: "Steve Simon"
source: new
date: "2021-10-09"
categories:
- Blog post
tags:
- Website details
output: html_document
---

>>>>

---
title: "First steps with blogdown"
author: "Steve Simon"
source: new
date: "2021-10-09"
categories:
- Blog post
tags:
- Website details
- Rmarkdown code
output: html_document
page_update: complete
---

### 2024-07-06 text/21/cubic-splines.Rmd
Updated rmd files

---
title: "Basics of cubic spline models"
author: "Steve Simon"
date: "2021-11-01"
categories:
- Recommendation
tags:
- Linear regression
output: html_document
---

>>>>

---
title: "Basics of cubic spline models"
source: new
author: "Steve Simon"
date: "2021-11-01"
categories:
- Recommendation
tags:
- Linear regression
- Rmarkdown graphs
output: html_document
page_update: complete
---

### 2024-07-06 text/21/dark-side.Rmd
Updated rmd files

---
title: "The dark side of big data"
source: new
date: "2021-10-28"
categories:
- Blog post
tags:
- Data science
- Incomplete page
output: html_document
---

>>>>

---
title: "The dark side of big data"
source: new
date: "2021-10-28"
categories:
- Blog post
tags:
- Data science
- Incomplete page
- Rmarkdown graphs
output: html_document
page_update: complete
---

### 2024-07-06 text/21/direct-standardization.Rmd
Updated rmd files

---
title: "Direct standardization of mortality rates"
author: "Steve Simon"
source: new
date: "2021-09-20"
categories:
- Blog post
tags:
- Epidemiology
output: html_document
---

>>>>

---
title: "Direct standardization of mortality rates"
author: "Steve Simon"
source: new
date: "2021-09-20"
categories:
- Blog post
tags:
- Epidemiology
- Incomplete pages
- Rmarkdown graphs
output: html_document
page_update: complete
---

### 2024-07-06 text/21/glm-deviance.Rmd
Updated rmd files

---
title: "Deviance in a generalized linear model"
author: "Steve Simon"
source: new
date: "2021-09-20"
categories:
- Blog post
tags:
- Generalized linear model
output: html_document
---

>>>>

---
title: "Deviance in a generalized linear model"
author: "Steve Simon"
source: new
date: "2021-09-20"
categories:
- Blog post
tags:
- Generalized linear model
- Rmarkdown graphs
output: html_document
page_update: complete
---

### 2024-07-06 text/21/glm-diagnostics.Rmd
Updated rmd files

---
title: "Diagnostics for a generalized linear model"
author: "Steve Simon"
source: new
date: "2021-10-18"
categories:
- Blog post
tags:
- Generalized linear model
output: html_document
---

>>>>

---
title: "Diagnostics for a generalized linear model"
author: "Steve Simon"
source: new
date: "2021-10-18"
categories:
- Blog post
tags:
- Generalized linear model
- Rmarkdown graphs
output: html_document
page_update: complete
---

### 2024-07-06 text/21/hurricane-frequencies.Rmd
Updated rmd files

---
title: "Overfitting example using hurricane frequencies"
author: "Steve Simon"
source: new
date: "2021-12-11"
categories:
- Blog post
tags:
- Generalized linear model
output: html_document
---

@@

```{r setup, echo=FALSE}
suppressMessages(suppressWarnings(library(broom)))
suppressMessages(suppressWarnings(library(dplyr)))
suppressMessages(suppressWarnings(library(ggplot2)))
suppressMessages(suppressWarnings(library(knitr)))
suppressMessages(suppressWarnings(library(magrittr)))
knitr::opts_chunk$set(echo=FALSE)
```

@@

```{r read1}
fn <- "https://dasl.datadescription.com/download/data/3279"
raw_data <- read.delim(file=fn, header=TRUE, sep="\t")
raw_data[1:8, ]
```

@@

```{r read2}
raw_data[9:16, ]
```

@@

```{r plot}
df <- data.frame(x=seq(1855, 1995, by=10), y=raw_data$Count[1:15])
ggplot(df, aes(x, y)) + 
  geom_point() -> point_plot
plot(point_plot)
```

@@

```{r poly1}
add_trend <- function(point_plot, df, degree) {
  x_grid <- data.frame(x=seq(1855, 2005, by=0.1))
  lm(y~poly(x, degree), data=df) %>%
    augment(newdata=x_grid) -> yhat
  yhat_2005 <- filter(yhat, x==2005)
  prediction <<- yhat_2005$.fitted
  point_plot +
    geom_line(data=yhat, aes(x, .fitted)) +
    geom_label(
      data=yhat_2005, 
      aes(x, .fitted, label=round(.fitted, 1)))
}
add_trend(point_plot, df, 1)
```

@@

```{r poly2}
add_trend(point_plot, df, 2)
```

@@

```{r poly3}
add_trend(point_plot, df, 3)
```

@@

```{r poly4}
add_trend(point_plot, df, 4)
```

@@

```{r poly5}
add_trend(point_plot, df, 5)
```

@@

```{r poly6}
add_trend(point_plot, df, 6)
```

@@

```{r poly7}
add_trend(point_plot, df, 7)
```

@@

```{r poly8}
add_trend(point_plot, df, 8)
```

@@

```{r poly9}
add_trend(point_plot, df, 9)
```

@@

```{r poly10}
add_trend(point_plot, df, 10)
```

@@

```{r poly11}
add_trend(point_plot, df, 11)
```

@@

```{r poly12}
add_trend(point_plot, df, 12)
```

@@

```{r poly13}
add_trend(point_plot, df, 13)
```

@@

```{r poly14}
add_trend(point_plot, df, 14)
```

@@

```{r reset}
knitr::opts_chunk$set(echo=TRUE)
knitr::opts_chunk$set(eval=FALSE)
```

```{r setup}
```

@@

```{r read1}
```

```{r read2}
```

@@

```{r plot}
```

@@

```{r poly1}
```

@@

```{r poly2}
```

```{r poly3}
```

```{r poly4}
```

```{r poly5}
```

```{r poly6}
```

```{r poly7}
```

```{r poly8}
```

```{r poly9}
```

```{r poly10}
```

```{r poly11}
```

```{r poly12}
```

```{r poly13}
```

```{r poly14}
```

>>>>

---
title: "Overfitting example using hurricane frequencies"
author: "Steve Simon"
source: new
date: "2021-12-11"
categories:
- Blog post
tags:
- Generalized linear model
- Rmarkdown graphs
output: html_document
page_update: complete
---

@@

```{r hurricane-frequencies-01, echo=FALSE}
suppressMessages(suppressWarnings(library(broom)))
suppressMessages(suppressWarnings(library(dplyr)))
suppressMessages(suppressWarnings(library(ggplot2)))
suppressMessages(suppressWarnings(library(knitr)))
suppressMessages(suppressWarnings(library(magrittr)))
knitr::opts_chunk$set(echo=FALSE)
```

@@

```{r hurricane-frequencies-02}
fn <- "https://dasl.datadescription.com/download/data/3279"
raw_data <- read.delim(file=fn, header=TRUE, sep="\t")
raw_data[1:8, ]
```

@@

```{r hurricane-frequencies-03}
raw_data[9:16, ]
```

@@

```{r hurricane-frequencies-04}
df <- data.frame(x=seq(1855, 1995, by=10), y=raw_data$Count[1:15])
ggplot(df, aes(x, y)) + 
  geom_point() -> point_plot
plot(point_plot)
```

@@

```{r hurricane-frequencies-05}
add_trend <- function(point_plot, df, degree) {
  x_grid <- data.frame(x=seq(1855, 2005, by=0.1))
  lm(y~poly(x, degree), data=df) %>%
    augment(newdata=x_grid) -> yhat
  yhat_2005 <- filter(yhat, x==2005)
  prediction <<- yhat_2005$.fitted
  point_plot +
    geom_line(data=yhat, aes(x, .fitted)) +
    geom_label(
      data=yhat_2005, 
      aes(x, .fitted, label=round(.fitted, 1)))
}
add_trend(point_plot, df, 1)
```

@@

```{r hurricane-frequencies-06}
add_trend(point_plot, df, 2)
```

@@

```{r hurricane-frequencies-07}
add_trend(point_plot, df, 3)
```

@@

```{r hurricane-frequencies-08}
add_trend(point_plot, df, 4)
```

@@

```{r hurricane-frequencies-09}
add_trend(point_plot, df, 5)
```

@@

```{r hurricane-frequencies-10}
add_trend(point_plot, df, 6)
```

@@

```{r hurricane-frequencies-11}
add_trend(point_plot, df, 7)
```

@@

```{r hurricane-frequencies-12}
add_trend(point_plot, df, 8)
```

@@

```{r hurricane-frequencies-13}
add_trend(point_plot, df, 9)
```

@@

```{r hurricane-frequencies-14}
add_trend(point_plot, df, 10)
```

@@

```{r hurricane-frequencies-15}
add_trend(point_plot, df, 11)
```

@@

```{r hurricane-frequencies-16}
add_trend(point_plot, df, 12)
```

@@

```{r hurricane-frequencies-17}
add_trend(point_plot, df, 13)
```

@@

```{r hurricane-frequencies-18}
add_trend(point_plot, df, 14)
```

@@

```{r hurricane-frequencies-19}
knitr::opts_chunk$set(echo=TRUE)
knitr::opts_chunk$set(eval=FALSE)
```

```{r hurricane-frequencies-01}
```

@@

```{r hurricane-frequencies-02}
```

```{r hurricane-frequencies-03}
```

@@

```{r hurricane-frequencies-04}
```

@@

```{r hurricane-frequencies-05}
```

@@

```{r hurricane-frequencies-06}
```

```{r hurricane-frequencies-07}
```

```{r hurricane-frequencies-08}
```

```{r hurricane-frequencies-09}
```

```{r hurricane-frequencies-10}
```

```{r hurricane-frequencies-11}
```

```{r hurricane-frequencies-12}
```

```{r hurricane-frequencies-13}
```

```{r hurricane-frequencies-14}
```

```{r hurricane-frequencies-15}
```

```{r hurricane-frequencies-16}
```

```{r hurricane-frequencies-17}
```

```{r hurricane-frequencies-18}
```

### 2024-07-06 text/21/negative-binomial-regression.Rmd
Updated rmd files

---
title: "Working with negative binomial regression"
author: "Steve Simon"
source: new
date: "2021-08-30"
categories:
- Blog post
tags:
- Probability distributions
- Generalized linear model
output: html_document
---

@@

```{r setup}
suppressMessages(suppressWarnings(library(broom)))
suppressMessages(suppressWarnings(library(dplyr)))
suppressMessages(suppressWarnings(library(ggplot2)))
suppressMessages(suppressWarnings(library(foreign)))
suppressMessages(suppressWarnings(library(magrittr)))
```

@@

```{r bar-charts-n}
data.frame(x=0:25) %>%
  mutate(p=dnbinom(x,  2, 0.8)) %>%
  ggplot(aes(x,p)) +
    geom_col() +
    expand_limits(y=1) +
    ggtitle("Poisson probabilities with n=2, p=0.8")
data.frame(x=0:25) %>%
  mutate(p=dnbinom(x, 10, 0.8)) %>%
  ggplot(aes(x,p)) +
    geom_col() +
    expand_limits(y=1) +
    ggtitle("Poisson probabilities with n=10, p=0.8")
data.frame(x=0:25) %>%
  mutate(p=dnbinom(x, 50, 0.8)) %>%
  ggplot(aes(x,p)) +
    geom_col() +
    expand_limits(y=1) +
    ggtitle("Poisson probabilities with n=50, p=0.8")
```

@@

```{r bar-charts-p}
data.frame(x=0:25) %>%
  mutate(p=dnbinom(x,  2, 0.8)) %>%
  ggplot(aes(x,p)) +
    geom_col() +
    expand_limits(y=1) +
    ggtitle("Poisson probabilities with n=2, p=0.8")
data.frame(x=0:25) %>%
  mutate(p=dnbinom(x, 2, 0.5)) %>%
  ggplot(aes(x,p)) +
    geom_col() +
    expand_limits(y=1) +
    ggtitle("Poisson probabilities with n=2, p=0.5")
data.frame(x=0:25) %>%
  mutate(p=dnbinom(x, 2, 0.2)) %>%
  ggplot(aes(x,p)) +
    geom_col() +
    expand_limits(y=1) +
    ggtitle("Poisson probabilities with n=2, p=0.2")
```

@@

```{r}
library(MASS)
nb1 <- glm.nb(art ~ fem + ment + phd + mar + kid5, data = articles)
summary(nb1)
```

>>>>

---
title: "Working with negative binomial regression"
author: "Steve Simon"
source: new
date: "2021-08-30"
categories:
- Blog post
tags:
- Probability distributions
- Generalized linear model
- Rmarkdown graphs
output: html_document
page_update: complete
---

@@

```{r negative-binomial-regression-01}
suppressMessages(suppressWarnings(library(broom)))
suppressMessages(suppressWarnings(library(dplyr)))
suppressMessages(suppressWarnings(library(ggplot2)))
suppressMessages(suppressWarnings(library(foreign)))
suppressMessages(suppressWarnings(library(magrittr)))
```

@@

```{r negative-binomial-regression-02}
data.frame(x=0:25) %>%
  mutate(p=dnbinom(x,  2, 0.8)) %>%
  ggplot(aes(x,p)) +
    geom_col() +
    expand_limits(y=1) +
    ggtitle("Poisson probabilities with n=2, p=0.8")
data.frame(x=0:25) %>%
  mutate(p=dnbinom(x, 10, 0.8)) %>%
  ggplot(aes(x,p)) +
    geom_col() +
    expand_limits(y=1) +
    ggtitle("Poisson probabilities with n=10, p=0.8")
data.frame(x=0:25) %>%
  mutate(p=dnbinom(x, 50, 0.8)) %>%
  ggplot(aes(x,p)) +
    geom_col() +
    expand_limits(y=1) +
    ggtitle("Poisson probabilities with n=50, p=0.8")
```

@@

```{r negative-binomial-regression-03}
data.frame(x=0:25) %>%
  mutate(p=dnbinom(x,  2, 0.8)) %>%
  ggplot(aes(x,p)) +
    geom_col() +
    expand_limits(y=1) +
    ggtitle("Poisson probabilities with n=2, p=0.8")
data.frame(x=0:25) %>%
  mutate(p=dnbinom(x, 2, 0.5)) %>%
  ggplot(aes(x,p)) +
    geom_col() +
    expand_limits(y=1) +
    ggtitle("Poisson probabilities with n=2, p=0.5")
data.frame(x=0:25) %>%
  mutate(p=dnbinom(x, 2, 0.2)) %>%
  ggplot(aes(x,p)) +
    geom_col() +
    expand_limits(y=1) +
    ggtitle("Poisson probabilities with n=2, p=0.2")
```

@@

```{r negative-binomial-regression-01}
library(MASS)
nb1 <- glm.nb(art ~ fem + ment + phd + mar + kid5, data = articles)
summary(nb1)
```

### 2024-07-06 text/21/poisson-inferences.Rmd
Updated rmd files

---
title: "Working with the Poisson distribution"
author: "Steve Simon"
source: new
date: "2021-08-30"
categories:
- Blog post
tags:
- Probability distributions
output: html_document
---

>>>>

---
title: "Working with the Poisson distribution"
author: "Steve Simon"
source: new
date: "2021-08-30"
categories:
- Blog post
tags:
- Probability distributions
- Rmarkdown graphs
output: html_document
page_update: complete
---

### 2024-07-06 text/21/poisson-regression.Rmd
Updated 15/files-for-r-class
Updated rmd files

---
title: "Working with Poisson regression"
author: "Steve Simon"
source: new
date: "2021-08-30"
categories:
- Blog post
tags:
- Probability distributions
output: html_document
---

>>>>

---
title: "Working with Poisson regression"
author: "Steve Simon"
source: new
date: "2021-08-30"
categories:
- Blog post
tags:
- Probability distributions
- Rmarkdown graphs
output: html_document
page_update: complete
---

### 2024-07-06 text/21/quasi-likelihood.Rmd
Updated rmd files

---
title: "Quasi-likelihood models"
author: "Steve Simon"
source: new
date: "2021-09-20"
categories:
- Blog post
tags:
- Generalized linear model
output: html_document
---

>>>>

---
title: "Quasi-likelihood models"
author: "Steve Simon"
source: new
date: "2021-09-20"
categories:
- Blog post
tags:
- Generalized linear model
- Rmarkdown graphs
output: html_document
page_update: complete
---

### 2024-07-06 text/21/read-acs-data.Rmd
Updated rmd files

---
title: "Reading information from the American Community Survey into R"
source: new
date: "2021-09-29"
categories:
- Recommendation
tags:
- Website details
output: html_document
---

>>>>

---
title: "Reading information from the American Community Survey into R"
source: new
date: "2021-09-29"
categories:
- Recommendation
tags:
- Rmarkdown graphs
- Website details
output: html_document
page_update: complete
---
